random forest and lme

### 2020-04-10 src/modeling - 550/rf.Rmd

```{r}
dat <- readr::read_delim("test_train_data.txt", delim = ",", col_types = "ciccdddddc")
dat$municipality <- as.factor(dat$municipality)

@@

train <- dat %>%  filter(test.train == "train") 
test <- dat %>%  filter(test.train == "test")
```

@@

rf.mill <- randomForest(
  mill.rate ~  tax.class + municipality + total.assessment + past.mill,na.action = na.omit, mtry = 4,
  data=train, ntree=500
)
#Evaluate variable importance
importance(rf.mill)
varImpPlot(rf.mill)

@@

>>>>

```{r}
dat <- readr::read_delim("test_train_data.txt", delim = ",", col_types = "ciccdddddc")
train <- readr::read_delim("train_data.txt", delim = ",", col_types = "ciccddddd")
test <- readr::read_delim("test_data.txt", delim = ",", col_types = "ciccddddd")
dat$municipality <- as.factor(dat$municipality)

@@

notwant <- c("CA-BC-003-6500000", "CA-BC-223-00100030000", "CA-BC-227-0000020000", "CA-BC-234-01001006", "CA-BC-301-0000001", "CA-BC-315-00001000","CA-BC-316-010012122009", "CA-BC-336-00001000", "CA-BC-338-1000004884000", "CA-BC-556-00001000", "CA-BC-727-03025100", "CA-BC-757-05141000", "CA-BC-759-000147000", "CA-BC-760-001203000", "CA-BC-765-00002001", "CA-BC-771-00003000")
train <- dat %>%  filter(test.train == "train" & !PIC %in% notwant)
test <- dat %>%  filter(test.train == "test")
```

@@

rf.mill <- randomForest(
  mill.rate ~  tax.class + municipality + total.assessment + past.mill,na.action = na.omit, mtry = 4,
  data=train, ntree=500
)

save(rf.mill, file = "~/Desktop/git_docs/RealEstate/src/shiny_app/rf.mill.rda")
#Evaluate variable importance
importance(rf.mill)
varImpPlot(rf.mill)

@@

# Linear Regression
```{r}
lm.as <- lm(
  next.assess ~ PIC + tax.class + municipality + total.assessment + mill.rate, na.action = na.omit, data=train)

predict(lm.as, test)
```
